%-------------------------
% Resume in Latex
% Author : Priyanshu Vishnoi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Priyanshu Vishnoi} \\ \vspace{1pt}
    \small 7500237607 $|$ \href{mailto:pv990@outlook.com}{\underline{pv990@outlook.com}} $|$ 
    \href{https://www.linkedin.com/in/priyanshu-vishnoi-53b816169}{\underline{linkedin.com}} $|$
    \href{https://github.com/priyanshuvishnoi}{\underline{github.com}}
\end{center}

Full Stack Developer with 5 years of experience building scalable web applications. Expert in \textbf{Java (Spring Boot)} and \textbf{Angular} ecosystems, with foundational experience in React. Proven track record in \textbf{event-driven microservices}, CI/CD automation with \textbf{Jenkins}, and container orchestration using \textbf{Kubernetes} and \textbf{OpenShift}.

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, JavaScript, TypeScript, SQL} \\
     \textbf{Frameworks}{: Spring Boot, Angular, RxJS} \\
     \textbf{Cloud \& DevOps}{: Jenkins, SonarQube, Kubernetes, OpenShift, Docker, AWS} \\
     \textbf{Databases \& Tools}{: MongoDB, PostgreSQL, Apache Kafka, D3.js, Redis, Git, JPA, JasperReports} \\
    }}
 \end{itemize}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Senior Analyst}{Nov 2024 -- Present}
      {Accenture}{Mumbai, MH}
      \resumeItemListStart
        \resumeItem{Built an \textbf{event-driven microservices architecture} using \textbf{Spring Boot} and \textbf{Apache Kafka} to automate retirement plan migrations for a major US financial client.}
        \resumeItem{Designed an \textbf{orchestration service} to manage asynchronous workflows, dynamically processing account data and business logic for \textbf{thousands of users}.}
        \resumeItem{Managed \textbf{distributed transactions} to securely migrate participant funds, active loans, and contracts between plans.}
        \resumeItem{Created a reporting microservice to automatically generate Excel (.xlsx) audit reports, processing \textbf{100,000+ records} per migration.}
        \resumeItem{Orchestrated containerized deployments using \textbf{Kubernetes} and \textbf{OpenShift}, and managed \textbf{Jenkins CI/CD pipelines} with \textbf{SonarQube} to enforce code quality.}
      \resumeItemListEnd

    \resumeSubheading
      {Systems Engineer}{Oct 2021 -- Nov 2024}
      {Tata Consultancy Services}{New Delhi, DL}
      \resumeItemListStart
        \resumeItem{Built interactive maps and complex data visualizations using \textbf{D3.js} to analyze geographical datasets with \textbf{10,000+ data points}.}
        \resumeItem{Led the end-to-end development of \textbf{4 core microservices} for a complex enterprise application.}
        \resumeItem{Developed advanced UI features in \textbf{Angular}, including virtual scrolling, language translation, and complex reactive forms.}
        \resumeItem{Implemented \textbf{Web Workers} for CPU-intensive background tasks like CSV generation, maintaining \textbf{100\% UI responsiveness}.}
        \resumeItem{Improved system performance using \textbf{Multithreading} to process large datasets in parallel, reducing page load times by \textbf{50\%}.}
        \resumeItem{Generated complex financial reports using \textbf{JasperReports} and built custom identity systems using \textbf{PostgreSQL} sequences.}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Web Developer Intern}{June 2020 -- Aug 2020}
      {AVILAKSH E-SERVICE LLP}{New Delhi, DL}
      \resumeItemListStart
        \resumeItem{Built a responsive admin dashboard using \textbf{React} and \textbf{Bootstrap} to improve internal data management efficiency.}
        \resumeItem{Integrated \textbf{RESTful APIs} using Axios to seamlessly manage product inventory and user order data.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Containerized Full-Stack To-Do Application} $|$ \emph{Angular, Spring Boot, K8s, Jenkins}}{}
      \resumeItemListStart
        \resumeItem{Architected a full-stack application utilizing an \textbf{Angular} frontend, \textbf{Spring Boot} backend, and \textbf{MongoDB}.}
        \resumeItem{Configured a \textbf{Jenkins CI/CD pipeline} with \textbf{SonarQube} for automated testing and deployed to a local \textbf{Kubernetes} cluster (Minikube).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Inderprastha Engineering College}{Ghaziabad, UP}
      {Bachelor of Technology in Computer Science \& Engineering}{Aug 2017 -- Aug 2021}
  \resumeSubHeadingListEnd

\end{document}
